### 2022-07-23 paper/akweury/document.tex
fix a bug

The network concatenate the image and the light together

>>>>

With the help of an extra image-light encoder, the network gained more information of the object surface, which is supposed to predict the surface normal more accurate. In this scenario, the output is still the surface normal, thus the training loss can be the same as GCNN model.
